Self Regulation Ontology Retest Analyses

### 2018-06-06 code/SRO_Retest_Analyses.Rmd
added meaningful vars file

@@

>>>>

NOTE: THIS MIGHT GIVE A FALSE SENSE OF HOW GOOD EACH TASK IS. SEE MEANINGFUL VARIABLES ANALYSES FOR TASKS.

@@

The above averaging of reliability estimates for all measures of tasks might not be the best way to look at how reliable a task is.

Not all measures for which we have calculated reliability estimates are measures that are used in the literature for these tasks

Dealing with this:
using the measures you found in the literature
using ian's function
